### 2022-04-15 paper/localpsf.tex
updates to paper

Given $(y,x)\in \Omega \times \Omega$, let
\begin{equation*}
	z_i := y - \mu(x) + \mu(x_i), \qquad i=1,\dots,k,
\end{equation*}
where $\{x_i\}_{i=1}^k$ are the $k$ nearest sample points to $x$, excluding sample points $x_i$ for which $z_i \notin \Omega$. Here $k$ is a small user defined parameter; e.g., $k=10$. Further, let
\begin{equation}
\label{eq:fxyxp}
f_i := \frac{V(x)}{V(x_i)}\phi_{x_i}\left(z_i\right), \qquad i=1,\dots,k,
\end{equation}
Note that $f_i$ is well-defined, because $\phi_{x_i}\left(z_i\right)$ is defined if and only if $z_i \in \Omega$, and $V(x_i)>0$ by our sample point picking procedure in Section \ref{sec:sample_point_selection}. We approximate $\Phi(y,x)$ by interpolating the (point,value) pairs
\begin{equation}
\left(x_i, f_i\right), \qquad i=1,\dots,k,
\end{equation}
at the point $x$. The idea is that $\Phi(y,x) = f_i$ per the discussion in Section \ref{eq:local_mean_displacement_invariance}, so we approximate $\Phi(y,x)$ by interpolating the values $f_i$.

@@

Interpolation is performed using the following radial basis function scheme:
\begin{equation}
\Phi(y,x) \approx \widetilde{\Phi}(y,x) := \sum_{i=1}^k w_i~ b\left(\|x-x_i\|\right),
\end{equation}
where $b_i$ are radial basis functions and $w_i$ are weights. The vector of weights, $w = (w_1, w_2, \dots, w_k)^T$, is found as the solution to the $k \times k$ linear system
\begin{equation}
Bw = f,
\end{equation}
where $B \in \mathbb{R}^{k \times k}$ has entries
$
B_{ij} := b\left(\|x_i - x_j\|\right),
$
and $f \in \mathbb{R}^k$ has entries $f_i$ from \eqref{eq:fxyxp}. We use polyharmonic spline radial basis functions \cite{polyspline}:
\begin{equation}
b_i(r) := \begin{cases}
r^d, & d=1,3,5,\dots \\
r^d \log r, & d=2,4,6,\dots
\end{cases}
\end{equation}
for $r>0$, and $b_i(0):=0$. This yields the smoothest interpolant of the given points and values, in a least-squares sense. For more details on radial basis function interpolation and polyharmonic splines, see \cite{rbf}.

>>>>

Given $(y,x)\in \Omega \times \Omega$, let
\begin{equation*}
	z_i := y - \mu(x) + \mu(x_i), \qquad i=1,\dots,k,
\end{equation*}
where $\{x_i\}_{i=1}^k$ are the $k$ nearest sample points to $x$, excluding sample points $x_i$ for which $z_i \notin \Omega$. Here $k$ is a small user defined parameter; e.g., $k=10$. Further, let
\begin{equation}
\label{eq:fxyxp}
f_i := \frac{V(x)}{V(x_i)}\phi_{x_i}\left(z_i\right), \qquad i=1,\dots,k,
\end{equation}
Note that $f_i$ is well-defined, because $\phi_{x_i}\left(z_i\right)$ is defined if and only if $z_i \in \Omega$, and $V(x_i)>0$ by our sample point picking procedure in Section \ref{sec:sample_point_selection}. We approximate $\Phi(y,x)$ by interpolating the (point,value) pairs
\begin{equation}
\left(x_i, f_i\right), \qquad i=1,\dots,k,
\end{equation}
at the point $x$. The idea is that $\Phi(y,x) = f_i$ per the discussion in Section \ref{sec:local_mean_displacement_invariance}, so we approximate $\Phi(y,x)$ by interpolating the values $f_i$.

@@

Interpolation is performed using the following radial basis function scheme:
\begin{equation}
\Phi(y,x) \approx \widetilde{\Phi}(y,x) := \sum_{i=1}^k w_i~ b\left(\|x-x_i\|\right),
\end{equation}
where $b_i$ are radial basis functions and $w_i$ are weights. The vector of weights, $w = (w_1, w_2, \dots, w_k)^T$, is found as the solution to the $k \times k$ linear system
\begin{equation}
Bw = f,
\end{equation}
where $B \in \mathbb{R}^{k \times k}$ has entries
$
B_{ij} := b\left(\|x_i - x_j\|\right),
$
and $f \in \mathbb{R}^k$ has entries $f_i$ from \eqref{eq:fxyxp}. We use polyharmonic spline radial basis functions \cite{polyspline}:
\begin{equation}
b_i(r) := \begin{cases}
r^d, & d=1,3,5,\dots \\
r^d \log r, & d=2,4,6,\dots
\end{cases}
\end{equation}
for $r>0$, and $b_i(0):=0$. This yields the smoothest interpolant of the given points and values, in a least-squares sense. For more details on radial basis function interpolation and polyharmonic splines, see \cite{rbf}. The interpolation procedure is illustrate in Figure \ref{fig:rbf_interpolation}.

\begin{figure}
	\begin{subfigure}{0.49\textwidth}
		\centering
		\includegraphics[scale=0.22]{interpolation_rbf.pdf}
		\caption{}
	\end{subfigure}
	\begin{subfigure}{0.49\textwidth}
		\centering
		\includegraphics[scale=0.22]{interpolation_rbf_boundary.pdf}
		\caption{}
	\end{subfigure}
	\caption{(a) To compute the kernel entry $\Phi(y,x)$, we use radial basis functions to interpolate the values $\frac{V(x)}{V(x_i)}\phi_{x_i}(y-\mu(x)-\mu(x_i))$ for the $k$ nearest sample points $x_i$ to $x$. (b) We exclude sample points for which $y-\mu(x)_\mu(x_i)$ is outside of the domain.}
	\label{fig:rbf_interpolation}
\end{figure}
